Offshore Crabs/Hectare Modeling

### 2020-01-06 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
tweedie mod

#packages
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(patchwork)
library(broom)
library(statmod)
library(sf)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")

@@

overall_mean <- mean(seamap$Sapidus_Catch, na.rm = T)
percent_zeros <- seamap %>% filter(Sapidus_Catch == 0) %>% count()
station_count <- seamap %>% count()
```

>>>>

#packages
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(patchwork)
library(gridExtra)
library(broom)
library(statmod)
library(sf)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")

@@

overall_mean <- mean(seamap$CPUE_towspd, na.rm = T)
percent_zeros <- seamap %>% filter(Sapidus_Catch == 0) %>% count()
station_count <- seamap %>% count()
```

# Data Set Summary

 * Total Number of Stations = `r nrow(seamap)`

 * Starting in `r min(as.numeric(as.character(seamap$Survey_Year)))` and continuing through `r max(as.numeric(as.character(seamap$Survey_Year)))`

 * Total Sapidus Caught was `r sum(seamap$Sapidus_Catch, na.rm = T)`

 * Overall Frequency of Occurrence was `r mean(seamap$Crab_presence, na.rm = TRUE) * 100`

# Factor Summaries

## Yearly Summaries {.tabset .tabset-fade .tabset-pills}

**Overall Mean Catch Crabs/Hectare: `r overall_mean`**
**Stations with no catch: `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`**

```{r}
year_sums <- seamap %>% 
  group_by(Survey_Year) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(CPUE_towspd)),
            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
            `SD`              = sd(CPUE_towspd, na.rm = T),
            `Var`             = var(CPUE_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
  ungroup() %>% 
    mutate(Survey_Year        = factor(Survey_Year),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )

year_sums %>% select(Survey_Year, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
#knitr::kable(year_sums)
```

***

### Yearly Catch Plot

```{r}

year_plot_1 <- year_sums %>% 
  ggplot() +
    geom_col(aes(Survey_Year, `Mean Catch`)) +
    geom_errorbar(aes(x = Survey_Year, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  labs(x = "Survey Year",
       y = "Mean Catch (C. sapidus / Hectare)") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

year_plot_1
#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)

```

***

### Yearly Frequency of Occurrence

```{r}

year_plot_2 <- year_sums %>% 
  ggplot() +
    geom_col(aes(Survey_Year, `% Occurrence`)) +
    geom_errorbar(aes(x = Survey_Year, 
                      ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  size = .25) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Survey Year",
       y = "Percent Occurrence") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

year_plot_2
#ggsave(plot = year_plot_2, here("2019_edits/figures", "yearly_occurrence.png"), dpi = 600)

```

***

### Yearly Side-by

```{r}
year_plot_1 + year_plot_2
```

***

## Stat Zone Summaries {.tabset .tabset-fade .tabset-pills}

```{r}
#Assign Stat Zone from NMFS grid
szones <- read_sf("~/Dropbox/SEAMAP_2019/data/gis_files/NMFS_Fishing_Grids_GOM_2013.shp", 
                  crs = 4326)

# Add a better StatZone ID by spatial overlap
seamap <- seamap %>% 
  st_as_sf(coords = c("Start_Long", "Start_Lat"), crs = 4326, remove = FALSE) %>% 
  st_join(szones["StatZone"]) %>% 
  st_set_geometry(NULL) %>% 
  as.data.frame() %>% 
  dplyr::select(-STAT_ZONE) %>%  #Remove default/incorrect one
  mutate(StatZone = factor(StatZone))

szone_summary <- seamap %>% 
  filter(is.na(StatZone)      == FALSE) %>% 
  group_by(StatZone) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(CPUE_towspd)),
            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
            `SD`              = sd(CPUE_towspd, na.rm = T),
            `Var`             = var(CPUE_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(StatZone           = factor(StatZone),
           StatZone           = fct_rev(StatZone),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )

szone_summary %>% 
  select(StatZone, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
  knitr::kable()

```

***

### Stat Zone Catch Plot

```{r}

szones_plot_1 <- szone_summary %>% 
  ggplot() +
    geom_col(aes(StatZone, `Mean Catch`)) +
    geom_errorbar(aes(x = StatZone, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
  geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
  #annotate(geom = "text", x = 7, y = 2.0, label = "LA + MS") +
  #annotate(geom = "text", x = 16, y = 2.0, label = "East of Mobile Bay") +
  annotate(geom = "text", x = 16.5, y = -0.1, label = "East of Mobile Bay") +
  annotate(geom = "text", x = 8, y = -0.1, label = "LA & MS") +
  annotate(geom = "text", x = 2.5, y = -0.1, label = "Texas") +
    labs(x= "Statistical Zone",
         y = "Mean Catch (C. sapidus / Hectare)")

szones_plot_1 
#ggsave(plot = szones_plot_1, here("2019_edits/figures", "statzones_catch.png"), dpi = 600)

```

***

### Stat Zone Frequency of Occurrence

```{r}

szones_plot_2 <- szone_summary %>% 
  ggplot() +
    geom_col(aes(StatZone, `% Occurrence`)) +
    geom_errorbar(aes(x = StatZone, 
                      ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  size = .25) +
  geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
  geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
  annotate(geom = "text", x = 16.5, y = 0.75, label = "East of Mobile Bay") +
  annotate(geom = "text", x = 8, y = 0.75, label = "LA & MS") +
  annotate(geom = "text", x = 2.5, y = 0.75, label = "Texas") +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Statistical Zone",
       y = "Percent Occurrence")

szones_plot_2
#ggsave(plot = szones_plot_2, here("2019_edits/figures", "statzones_occurrence.png"), dpi = 600)
```

***

### Stat Zone Side-by

```{r}
szones_plot_1 + szones_plot_2
```

***

## Region Summary {.tabset .tabset-fade .tabset-pills}

```{r}
seamap <- seamap %>% 
  mutate(
    # region = ifelse(Start_Lat < 28.387595 & Start_Long < -96, "South Texas", "TX/LA"),
    #      region = ifelse(Start_Long > -89.2, "MS Bight", region),
    #      region = ifelse(Start_Long > -87.5, "FL", region),
    #      region = factor(region)
    region = ifelse(StatZone %in% seq("21", "18"), "Texas", "Louisiana"),
    region = ifelse(StatZone %in% seq("12", "10"), "MS Bight", region),
    region = ifelse(StatZone %in% seq("1", "9"), "Florida", region),
    region = factor(region, levels = c("Texas", "Louisiana", "MS Bight", "Florida"))
    )

#Output seamap analysis file
write_csv(seamap, 
          "~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019_analysis.csv", 
          col_names = TRUE)

region_summary <- seamap %>% 
  filter(is.na(region)      == FALSE) %>% 
  group_by(region) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(CPUE_towspd)),
            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
            `SD`              = sd(CPUE_towspd, na.rm = T),
            `Var`             = var(CPUE_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(region             = factor(region, 
                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
           #region             = fct_rev(region),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
    )

region_summary %>% 
  select(region, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
  knitr::kable()

```

***

### Regional Catch Plot

```{r}

region_plot_1 <- region_summary %>% 
  ggplot() +
    geom_col(aes(region, `Mean Catch`)) +
    geom_errorbar(aes(x = region, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
    labs(x= "Sampling Region",
         y = "Mean Catch (C. sapidus / Hectare)")

region_plot_1 
#ggsave(plot = region_plot_1, here("2019_edits/figures", "regions_catch.png"), dpi = 600)
```

***

### Regional Frequency of Occurrence

```{r}

region_plot_2 <- region_summary %>% 
  ggplot() +
    geom_col(aes(region, `% Occurrence`)) +
    geom_errorbar(aes(x = region, 
                      ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  size = .25) +
  # geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
  # geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
  # annotate(geom = "text", x = 16.5, y = 0.75, label = "East of Mobile Bay") +
  # annotate(geom = "text", x = 8, y = 0.75, label = "LA & MS") +
  # annotate(geom = "text", x = 2.5, y = 0.75, label = "Texas") +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Sampling Region",
       y = "Percent Occurrence")

region_plot_2
#ggsave(plot = region_plot_2, here("2019_edits/figures", "regions_occurrence.png"), dpi = 600)

```

***

### Regional Side-by

```{r}
region_plot_1 + region_plot_2
```

***

## Region - Season {.tabset .tabset-fade .tabset-pills}

```{r}
rs_summary <- seamap %>% 
  filter(is.na(region)      == FALSE) %>% 
  group_by(region, Season) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(CPUE_towspd)),
            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
            `SD`              = sd(CPUE_towspd, na.rm = T),
            `Var`             = var(CPUE_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(Season             = factor(Season, levels = c("Summer", "Fall")),
           region             = factor(region, 
                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
           #region             = fct_rev(region),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
    )

rs_summary %>% 
  select(region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
  knitr::kable()
```

***

### Region - Season Catch

```{r}
rs_plot_1 <- rs_summary %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = "Survey Year",
       y = "Mean Catch (C. sapidus / Hectare)") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

rs_plot_1 
```

***

### Region - Season FOO

```{r}

rs_plot_2 <- rs_summary %>% 
  ggplot(aes(region, `% Occurrence`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Survey Year",
       y = "Percent Occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

rs_plot_2

```

***

### Region - Season Side-by

```{r}

rs_plot_1 + theme(legend.position = "none") + rs_plot_2

```

***

## Seasonal Summary {.tabset .tabset-fade .tabset-pills}

```{r}

season_summary <- seamap %>% 
  group_by(Survey_Year, Season) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(CPUE_towspd)),
            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
            `SD`              = sd(CPUE_towspd, na.rm = T),
            `Var`             = var(CPUE_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(Survey_Year        = factor(Survey_Year),
           # StatZone         = factor(StatZone),
           # StatZone         = fct_rev(StatZone),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )

season_summary %>% select(Survey_Year, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
#knitr::kable(season_summary)
```

***

### Seasonal Catch Plot

```{r}

season_plot_1 <- season_summary %>% 
  ggplot(aes(Survey_Year, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = "Survey Year",
       y = "Mean Catch (C. sapidus / Hectare)") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

season_plot_1 
#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)

```

***

### Seasonal Frequency of Occurrence

```{r}

season_plot_2 <- season_summary %>% 
  ggplot(aes(Survey_Year, `% Occurrence`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Survey Year",
       y = "Percent Occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

season_plot_2

```

***

### Seasonal Side-by

```{r}
season_plot_1 + theme(legend.position = "none") + season_plot_2
```

***

## Combining Figures {.tabset .tabset-fade .tabset-pills}

### 1x2

```{r, message = FALSE, warning = FALSE, comment = NA}
year_plots <- grid.arrange(grobs = list(year_plot_1 + xlab(""), year_plot_2), nrow = 2, ncol = 1)
year_plots
season_plots <- grid.arrange(grobs = list(season_plot_1 + xlab(""), season_plot_2), nrows = 2, ncol = 1)
season_plots
szone_plots <- grid.arrange(grobs = list(szones_plot_1 + xlab(""), szones_plot_2), nrows = 2, ncol = 1)
szone_plots

```

### 3x2 A.

```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}
super_plot_tall <- grid.arrange(
  grobs = list(year_plot_1, 
               year_plot_2 + ylab(""),
               season_plot_1, 
               season_plot_2 + ylab(""),
               szones_plot_1, 
               szones_plot_2 + ylab("")), 
  nrow = 3)
#super_plot_tall
```

### 3x2 B.

```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}

super_plot_wide <- grid.arrange(
  grobs = list(year_plot_1 + xlab(""), 
               season_plot_1 + xlab("") + ylab(""), 
               szones_plot_1 + xlab("") + ylab(""),
               year_plot_2,            
               season_plot_2 + ylab(""), 
               szones_plot_2 + ylab("")),
  nrow = 2
)

#super_plot_wide
```

# Crab/hectare Models

## Tweedie Models {.tabset .tabset-pills}

Tweedie distributions are similar to a negative-binomial in their application for datasets that exhibit zero inflation. Tweedie models are applicable in cases where the response is continuous i.e. catch/area.

### Model 1a. 2000-2018 w/ interaction

This model uses crabs per hectare as the response over the period of 18 years (2000-2018). Data is limited to statzones that were consistently sampled over the time period (i.e. West of Mobile Bay).

```{r}
seamap <- seamap %>% rename_all(tolower)
seamap_west <- seamap %>% 
  filter(statzone != 12,
         statzone %in% 11:21)

mod1a <- glm(cpue_towspd ~ year_f + region + season + survey_design +  #Additive covariates
            year_f * region,                                           #Interaction terms
            family = tweedie(),
            data = seamap_west)

# summary(mod1a)
# 
# emmeans::emmip(mod1a, region ~ year_f) 
```

#### Model Summary

```{r}
tidy(mod1a) %>% 
  mutate(`signif.` = ifelse(p.value <= .05, "*", "")) %>% 
  kable()
```

#### Fit Diagnostics

```{r}
broom::glance(mod1a) %>% kable()
```

##### CPUE Timeline

```{r}
#Predicted abundance dataframe
mod1a.dat <- emmeans(mod1a, 
                        specs = "year_f" , 
                        by    = "region", 
                        type  = "response") %>% 
  as.data.frame()

#Try this
emm <- update(emmeans(m1, "am"), tran = "log")
summary(emm, type = "response")

#Standardize to mean
mean_pred <- mean(mod1a.dat$response)
mod1a.dat <- mod1a.dat %>% mutate(Std_Index = response/mean_pred,
                                CV = SE/response,
                                LCI = asymp.LCL/mean_pred,
                                UCI = asymp.UCL/mean_pred,
                                Year_n = as.numeric(as.character(year_f)))

#make scale_x_discrete breaks b/c ggplot is dumb
ystart <- min(as.numeric(seamap$survey_year))
yend   <- max(as.numeric(seamap$survey_year))
ynames <- lubridate::year(seq.Date(as.Date(paste(ystart), "%Y"), 
                   as.Date(paste(yend), "%Y"), 
                   by = "year"))

#ggplot of standardized index of abundance
p <- mod1a.dat %>% 
  ggplot(aes(year_f, response)) +
      geom_ribbon(aes(Year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
      geom_line(aes(Year_n, response, group = 1)) +
      geom_point(aes(Year_n, response)) +
      geom_hline(aes(yintercept = 0), color = "darkred", linetype = 2) +
      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
      xlab("") + ylab("Crabs per Hectare") +
      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
      facet_wrap(~region)
p

emmeans(mod1a, specs = "year_f", by = c("region", "season", "survey_design"))
```

## Negative Binomial Models {.tabset .tabset-fade .tabset-pills}
